Centralized Programming for Distributed Control Planes

### 2016-01-27 paper/introduction.tex
stuff

To evaluate the \sysname{} language and system, we have experimented with specifying policy
for several realistic data center and backbone networks and compared these specifications
with existing operating specifications. We have also
measured the performance of our compiler, demonstrating that our compilation
algorithms scale to topologies with several thousand routers.

>>>>

To evaluate the \sysname{} language and system, we have experimented with specifying policy
for several realistic data center and backbone networks and compared these specifications
with existing configurations. We have also
measured the performance of our compiler, demonstrating that our compilation
algorithms scale to topologies with several thousand routers.
